---
title: "Nevada Project 2022"
author: "Jasmin Fernandez Castillo (NAME PRONUNCIATION: Hazz-Mean, PRONOUNS: They/Them/Theirs"
date: "`r Sys.Date()`"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Description

- Frequencies of Voter Registration
- Data from 2018 to Current
- Per Party
- Per Assembly District

## Snippet of the Data

```{r }
library(knitr)
getwd()
CD<-read.csv("No_NA_Clean_AD_2018_22.csv")
kable(CD[1:10,], caption = 'Nevada Data')

```

## Data Source

- [Nevada WebSite](https://www.nvsos.gov/sos/elections/voters/voter-registration-statistics)

- [Code Location](https://github.com/jf2987/Nevada-Data-Cleaning)


## Democrats in the year of 2020

```{r}
CD_2020<-subset(CD, Year== 2020)
# https://www.youtube.com/watch?v=HPJn1CMvtmI

library(ggplot2)

ggplot(data=CD_2020, mapping=(aes(Month, Democrat)))+ geom_boxplot()+ scale_x_discrete(limits = c("January","February","March", "April", "May", "June", "July", "August", "September","October","November", "December"))

```

## Box Plot of Non.Partisans in the year of 2020
```{r}
# https://stackoverflow.com/questions/16588022/how-can-i-reorder-the-x-axis-in-a-plot-in-r
library(ggplot2)

ggplot(data=CD_2020, mapping=(aes(Month, Non.Partisan)))+ geom_boxplot()+ scale_x_discrete(limits = c("January","February","March", "April", "May", "June", "July", "August", "September","October","November", "December"))

```

## Box Plot per Assembly District year 2020

```{r}
library(ggplot2)
library(shiny)
# https://www.youtube.com/watch?v=HPJn1CMvtmI
ggplot(data=CD_2020, mapping=(aes(Assembly_District, Non.Partisan, colour=Month)))+ geom_point() + scale_x_discrete(limits = factor(c(1:42))) +scale_color_discrete(limits = c("January","February","March", "April", "May", "June", "July", "August", "September","October","November", "December"))

```

## Shiny Trial 

```{r}
library(ggplot2)
library(shiny)
library(dplyr)
# https://www.youtube.com/watch?v=HPJn1CMvtmI
server<-function(input, output, session){

data<-reactive({
  req(input$Month)
  df<-CD_2020 %>%filter(Month %in% input$Month)
})

output$plot <- renderPlot({
ggplot(data(), mapping=(aes(Assembly_District, Non.Partisan, colour=Month)))+ geom_point() + scale_x_discrete(limits = factor(c(1:42))) +scale_color_discrete(limits = c("January","February","March", "April", "May", "June", "July", "August", "September","October","November", "December"))
})

}
ui <-basicPage(
  h1("test"),
  selectInput(inputId = "Month", label = "Month", 
              list("January","February","March", "April", "May", "June", "July", "August", "September","October","November", "December")),
  plotOutput("plot")
)

shinyApp(ui=ui, server = server)

```


## Trials and Tribulations

- The data format varied Year to Year
- All data for 2018 downwards is in PDF Form
- There is a discrepancy between the Month and Year Noted for the Excel File and Hyper linked in the Webcite

```{r}

Discrepancy<-read.csv("Data_Check.csv")
## delete empty columns
library(purrr)
Discrepancy<-Discrepancy %>% discard(~all(is.na(.) | . ==""))

kable(Discrepancy[1:10,c(1,3)], caption = 'Discrepancies')

```



## Solutions
- Create a R script to Facilitate the Cleaning Process
- Convert PDF's into Excel Files VIA the Tabulizer Package

## Warning
- The Tabulizer Package Crashes the Latest Version of R Studio
- Tabulizer Package can, however, Be used with R without an IDE


## Results
- Data can be Used to explore Longitudinal Trends Pre and Post the Jan. 2020 Automatic Voter Registration in Nevada
- Data can be used to target Districts with the Most amounts of registered Democrats and Non-Partisans
- Data can also be used to note the change in Party for Voters
